---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PowerPlant

<!-- badges: start -->
<!-- badges: end -->

The goal of PowerPlant is to give insights on plant capacity, generation, ownership, and fuel type of global power plants

## Installation

You can install the released version of PowerPlant from [CRAN](https://CRAN.R-project.org) with:

``` r
# install.packages("PowerPlant")
devtools::install_github("athenamelia/PowerPlant")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(PowerPlant)
summary(PowerPlant)
```

## Analysis 
```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(mosaic)
knitr::opts_chunk$set(
  tidy=FALSE,     
  size="small")   
```

### a. What is the total electrical generating capacity for each fuel?

SOLUTION:

```{r message = FALSE, warning = FALSE}
PowerPlant %>% 
  group_by(primary_fuel) %>%
  summarize(total_cap = sum(capacity_mw)) %>% 
  arrange(desc(total_cap)) %>%
  select(primary_fuel, total_cap) %>%
  knitr::kable()

PowerPlant %>% 
  group_by(country_long) %>%
  summarize(total_cap = sum(capacity_mw)) %>% 
  arrange(desc(total_cap)) %>%
  select(country_long, total_cap) %>%
  head(6) %>%
  knitr::kable()
```

- Coal and Gas have the largest total electrical generating capacity at 1,999,520 and 1,472,694 megawatts respectively. Wave & Tidal and Storage have the lowest total eletrical generating capacity at 552.200 and 453.600 mw respectively. 

- China and the US have the largest electricity generation. 

### b) Geolocation of capacity of power plant: 

SOLUTION:

```{r message = FALSE, warning = FALSE}
PowerPlant <- PowerPlant %>%
  mutate(capacity_group = case_when(
                            capacity_mw < 100 ~ "very low",
                            capacity_mw < 5000 ~ "low",
                            capacity_mw < 10000 ~ "medium", 
                            capacity_mw > 10000 ~ "high"))
ggplot(
  data = PowerPlant, 
  aes(x = longitude, 
      y = latitude, 
      color = capacity_group)
  ) +
  geom_point(alpha = 0.5)

ggplot(
  data = PowerPlant, 
  aes(x = longitude, 
      y = latitude, 
      color = primary_fuel)
  ) +
  geom_point(alpha = 0.5)
```

- In the summary table, it shows that China and the US have the largest total electricity generation. However, when ploting the geolocation of those power plants after categorizing their capacity for eletricity generation into very low, low, medium and high groups, it shows that most countries have very low or low capacity. There are only a few countries in South America with medium capacity. 


